\documentclass{article} % use larger type; default would be 10pt
\usepackage{placeins}
\usepackage{tabularx}
\usepackage{booktabs} % for much better looking tables

\title{SE 3XA3: Problem Statement\\CraftMaster}
\author{Group 307, 3 Craftsmen\\
		Hongqing Cao 400053625\\
		Sida Wang	 400072157\\
		Weidong Yang 400065354}
\date{}

%\input{../Comments}

\begin{document}

\maketitle
\newpage
\FloatBarrier
\begin{table}[hp]
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Jan 22 & Hongqing & Initial upload\\
Jan 22 & Weidong & Spelling Check\\
Jan 22 & Hongqing & Fixing grammar issus\\
Jan 22 & Sida & Modification on Section 1.2\\
Jan 23 & Sida & Modification on Section 1.3\\
Jan 23 & Hongqing & Minor Modification on Section 1.3\\
Feb 11 & Hongqing & Renamed project\\
Mar 14 & Sida & Edited for Revision 1\\
\bottomrule
\end{tabularx}
\caption{Revision History} \label{TblRevisionHistory}
\end{table}
\FloatBarrier
\newpage
\section{Problem Statement}

\subsection{What problem are you trying to solve?}

Many children around the world are starting to play video games at a younger age. Unlike adults and teenagers, it is difficult for young children to find the right video games that are suitable for them to play. As software developers, we are trying to turn the reputable game, Minecraft, into an inspiring software game that will bring entertainment to the young generation and boost their creativity.

\subsection{Why is this an important problem?}

In the current video game market, most 3D video games contain violent content. The age limitation on some video games keeps children and teenagers away from them. Even the reputable game, Minecraft, is classified as \textbf{Fantasy Violence}\cite{ESRB} by ESRB and it is only recommended for individuals that are older than ten years old.

\subsection{What is the context of the problem you are solving?}

As a proposal, we plan to provide a 3D sandbox game, CraftMaster, to eliminate all violent content and allow people of all ages to enjoy the fun of building blocks in a virtual world. The entire package, including source code and the executable file, will be compressed into a zip file. The executable game will be available on a desktop PC with either Windows or Linux and it allows a more accessible way to play the game where the previous design can only be executed by the command in terminal.



\newpage
\begin{thebibliography}{9}
\bibitem{ESRB} 
“Ratings Guide,” 
\textit{ESRB Ratings}. 
Available: https://www.esrb.org/ratings-guide/. [Accessed: 14-Mar-2020]
\end{thebibliography}
%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}
